Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-07-04 analysis/article/paper.tex
repair table lables & some writing

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal of Behavioral and Experimental Economics}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation},
  pdfauthor={Hauke Roggenkamp},
  pdfkeywords={Public goods, Dynamic
games, Reproducibility, Generalizability, Online Experiment, Climate
change mitigation},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    Public goods \sep Dynamic
games \sep Reproducibility \sep Generalizability \sep Online
Experiment \sep 
    Climate change mitigation
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. Opting for environmentally friendly policies today not only
reduces carbon dioxide emissions immediately but also helps us to reach
the Paris climate targets tomorrow. Deferring these policies, may not
necessarily prevent us from reaching these targets, but it requires more
effort in the future compared to a path that includes immediate action
\citep{HaenselEtAl2022}. Aiming at certain goals, today's actions (or
the omission thereof) not only affect intermediate outcomes but also the
number of paths one can choose from that lead to that specific goal.

Public good (or public bad) games---although often intended to inform
climate policies
\citep[e.g.][]{MilinskiEtAl2006, TavoniEtAl2011, Hauser2014, BrickEtAl2015, GomezEtAl2018, CalzolariEtAl2018, CookEtAl2019}---miss
these temporal interdependencies simply because participants have the
same set of actions in each period. Accordingly, participants' actions
in a given period do not affect their action space in subsequent
periods. To see the lack of realism, consider carbon dioxide emissions,
where the current stock will last for well over a millennium
\citep{Inman2008, CalzolariEtAl2018}. Playing with fresh endowments in
each period is as if one could just undo carbon dioxide emissions at no
cost.

A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
hereafter, GMTV]{GMTV2017} as well as Stefan Große (unpublished), shows
that it is fairly simple to add this element of realism. They
incorporate interdependencies into a \emph{dynamic} public goods game
(dPGG) by defining endowments as the income of previous periods.
Consequently, participants' actions in a given period affect their
number of actions in subsequent periods: the more (less) they earn now,
the more (less) they can contribute in the next period. Importantly,
this modification qualitatively yields the same rational predictions as
the static game (i.e.~free-riding and the under-provision of the public
good). It is thus, equally well suited to study dilemma situations.

Because there is surprisingly little experimental research on
interdependencies\footnote{See e.g. \citet{BattagliniEtAl2016},
  \citet{Rockenbach2017} or \citet{Moser2019}.}, I reproduced one of
GMTVs' treatments to compare dynamics across (in)experienced samples to
investigate its generalizability. \citet{GKLS2020} find that static
public goods games do not generalize well to real-world climate action.
They also find that generalizability depends on the structural
resemblance of the public goods game with the context of climate change
mitigation: Greater resemblance improves generalizability. Because
GMTVs' dynamic setting has a more realistic property---namely,
interdependencies---one would expect it to be better suited to inform
public policy. To test this intuition, I not only ran the experiment
with different samples but also observed the participants' behavior in
voluntary climate actions (VCA).\footnote{The VCA is a (charitable)
  dictator game where each participant is a dictator dividing her budget
  between herself and some organization linked to the reduction of CO2
  emissions. \citet{EckelGrossman1996} were the first to implement a
  charitable dictator game observing contributions of 30\% of the
  endowments. Like \citet{GKLS2020}, \citet{CarpenterEtAl2008} report
  that students make lower contributions to charity than community
  members.} This yielded a setting similar to the one of
\citet{GKLS2020}, which allows me to analyze how behavior in the
abstract game translates into real-world action across samples. This
research shows that the dynamic setting \emph{does not} add any advances
to the generalizability of results.

\citet{AGM2018} conducted static public goods games in the lab and on
MTurk to draw (and report) lessons from online experimentation. This
study extends this literature \citetext{\citealp[see,
e.g.,][\citet{AmirEtAl2012}]{KrantzEtAl1997}; \citealp{KleinEtAl2014}; \citealp{PaolacciChandler2014}; \citealp{GoodmanPaolacci2017}; \citealp{SnowbergYariv_2021}; \citealp{GuptaRigottiWilson_2021}; \citealp{BusoEtAl2021}}
by focusing on an \emph{inconvenient} sample (i.e.~one that is a
completely inexperienced sample \citep[see also][]{BenndorfEtAl2017}
that has not been exposed to interactive experiments before) playing a
computationally more complex game during a time that was characterized
by more inattentiveness in online samples
\citep{ArecharRand2021, PeytonEtAl2022}. This required me to design
robust (and thus, more complex) software to minimize attrition. I
collected para data \citep[ p.~12]{Parsons2022}---which capture screen
time and survey navigation, for instance---to assess the desired fluency
and feasibility of the experiment. Like \citet{AGM2018}, this research
is of practical relevance as it reports on the robust design that made
the dynamic game feasible.

@@

Now, 20 years later, we accustom ourselves to mechanisms designed to
unravel the fuzzy back-and-forth between exploratory and confirmatory
research. Prominently, pre-registrations and pre-analysis plans (PAP)
\citep[see, e.g.,][]{BrodeurEtAl2022} were established to tie the
researchers' hands with respect to p-hacking and ex-post theorizing when
doing confirmatory research---reducing observable discrepancies between
Daryl Bem's above-mentioned (a) and (b).

While pre-registrations and PAPs could help to make empirical sciences
more credible, they come at costs that are discussed by
\citet{Olken2015}, \citet{PageEtAl2021}, as well as \citet{Krishna2021},
\citet{SimmonsEtAl2021}, and \citet{PhamEtAl2021}. One important concern
is that strict pre-registrations may severely discount any additional
analysis of the data inspired by surprise results. In practice, there
are at least two ways to approach that problem: First, one could (and
should) add unforeseen analyses to the article but label them as
exploratory. Second, one could write a minimal pre-registration leaving
enough degrees of freedom for the researcher to incorporate such
surprises without further notice. The key difference between the two
approaches is the deliberate omission of transparency.

For the field of neuropsychopharmacology \citet{WaldronAllen2022}
document that the depth of pre-registrations differs indeed: it is
spanning from notes on hypotheses only to fully specified, detailed
experimental protocols with accompanying power analyses and sampling
plans. Treating all pre-registrations equally may thus lead to an
adverse effect: If one can acquire the \emph{`pre-registered'} label
with minimal effort and maximum flexibility, the label itself may run
into danger to become worthless and to miss the target of making science
more credible.

This erosion of credibility can be avoided by the means of
transparency---not because transparency can tighten the ties but because
it facilitates scrutiny, policing
\citep[see][]{AnkelPetersFialaNeubauer2023} and forensics \citep[see,
e.g.,][]{SimonsohnEtAl2023}: transparent research practices make it
easier for others to track and understand a researcher's reaction to
surprises in the data, which, in turn, gives the researcher more
flexibility to react to these surprises. As additional transparency is
associated with additional effort, I propose version control as a
natural and easy-to-implement solution augmenting pre-registrations.

Contemporary experimental research is, to a certain degree, a
computational science: experiments often require complex software and
the analysis thereof can result in complicated scripts. In addition,
much research is carried out in collaborative efforts. For these reasons
alone, it makes sense to implement version control systems such as
GitHub and GitLab as well as OSF (albeit less powerful) that ensure that
files are stored consistently and that changes are tracked. When these
systems are implemented in the whole research process, one can archive
different states of the software and visualize differences between
different states. For instance, one can archive the analysis before and
after the data was collected or the experimental software used in a
pilot and the eventual experiment. Importantly, one can keep projects
private and change their visibility to public only after the
corresponding article is accepted for publication. Taken together, these
features \emph{automatically} enhance transparency and facilitate
scrutiny, policing, and forensics whilst also making software
development and collaboration more efficient. As a consequence, the
implementation and eventual disclosure of version control come not only
with meta-scientific but also with organizational benefits.

The experiment reported in this article qualifies for the
\emph{`pre-registered'} label at first glance: The analysis was
pre-registered in the American Economic Association's RCT Registry
\citep{preregistration}. Further, I pre-registered the exact analyses I
planned to run (PAP) when I designed the experiment on
\href{https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R}{GitHub}.\footnote{bit.ly/3Pnak5H.
  To run the code, you need to execute the .Rmd files in this repository
  in the order that is indicated by file names. Detailed instructions
  can be found in the README file accompanying the analysis scripts.}

At second glance, the analysis that made the most sense after having
collected the data and that is reported here is a little different
though: Because the more representative subject pool was exhausted
earlier than expected, I recruited students which opened up a new
research direction: assessing generalizability. Hence, this article
combines both confirmatory as well as exploratory research.

Accordingly, I edited many of the analysis scripts.\footnote{The source
  code of this document contains the analysis and can be found
  \href{https://github.com/Howquez/GMTV/blob/main/analysis/article/paper.qmd}{here}:
  https://bit.ly/43LCyLw} However, because the originally planned
analysis code is archived and reproducible, these changes are
transparent. Importantly, I followed a literate programming approach
\citep{Knuth_1984, AkhtarYe_2023}. Hence, all documents needed to
analyze the data and to write the report stem from the same source. This
establishes consistence between the commands one tells the statistical
software to do and the explanation one tells human beings one told the
statistical software to do. As such, (a), (b), and the transition from
(a) to (b) are not only transparent but also comprehensible.

@@

In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
well as a \emph{scientific} reproduction\footnote{In fact,
  \citet{Hamermesh2007} uses the term \emph{replication} instead of
  \emph{reproduction}. The reason I deviate is that I do not compare
  different treatments with each other to \emph{replicate} a treatment
  effect. Instead, I \emph{reproduce} the results of one specific
  treatment arm.} of one treatment of GMTVs' dynamic public goods game.
The pure reproduction re-analyzes the original data.
\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
\href{}{the errors I identified} in the original paper. The scientific
reproduction, where I utilize a different sample drawn from a different
population in a different situation, is described in the following
sections.

@@

Like GMTV I employ a real giving task after the abstract game.
Specifically, I employed a (charitable) dictator game where each
participant is a dictator dividing her budget between herself and some
organization. Whereas GMTV chose \emph{Doctors without Borders} as a
receiver, I chose another organization in another context: like
\citet{GKLS2020}, I employed a VCA, where participants could donate any
amount of their earnings to offset carbon dioxide (that is, retire
emission permits from the EU ETS).\footnote{Importantly,
  \citet{GKLS2020} made the VCA decision with a fresh endowment
  \emph{before} they played the abstract game. I deviate from their
  procedure to match GMTVs' procedure.} To ensure that each participant
had the same basic level of information about the impact of their
decision, I provided some basic information about the mechanism. The
information also highlighted that the mitigation came into operation on
a European level. Finally, I informed the participants that the
documentation of individual and aggregate contributions was to be posted
immediately after the conclusion of the sessions online. To avoid
privacy or social image concerns, participants learned their unique and
random IDs, which they needed to identify their individual
contributions. The document certified that their contributions have been
used to offset
\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
tons} of carbon dioxide emissions.

@@

Throughout this paper, I will compare the results of my experiment with
the results of GMTVs' NOPUNISH 10 Period treatments. I am thus,
referring to three different samples utilized at two points in time: the
University of Nottingham's students (in late 2012), Hamburg's citizens,
and the University of Hamburg's students (both in July 2021).
Table~\ref{tbl-sample-properties} gives an overview.

@@

I chose oTree \citep{oTree} to implement the experiment because it is
open-source, well-documented, and very flexible. Its
\href{https://getbootstrap.com/}{Bootstrap} (a powerful frontend
toolkit) integration allowed me to make the graphical user interface
interactive, appealing, and easy to navigate. The
\href{https://www.highcharts.com/}{Highcharts library} made it easy to
visualize results and communicate dynamics. Insofar, oTree served as a
good tool to enhance the participants' user experience and thus, to make
dropouts less likely.

Which features were required to handle dropouts? First, participants had
to be matched to form a group \emph{after} comprehension questions were
answered successfully. Importantly, participants were grouped by the
order they answered these questions to reduce waiting times. While
waiting for other players to form the group, the participants saw a
wait-page informing them that they are waiting for other participants to
arrive and that they do not have to wait for longer than 10 minutes. The
screen also informed them that they would receive a \emph{patience
bonus} of one Euro after the expiration of that time (or what was left
of it). Second, participants only had 10 minutes to make the first
contribution and 4 minutes for the remaining contributions. After this
time expired, participants were replaced by bots that made random
contributions. In this case, the remaining group members were informed
about the replacement. Both features were implemented to limit wait
times and boredom for other participants. Section~\ref{sec-feasibility}
shows that the first feature became effective in some cases, whereas the
second feature did not.

@@

While I stuck to GMTVs' protocol as close as possible, I deviated in a
few aspects. First, the instructions were German and also covered topics
inherent to the online setting (dropouts and bots, for instance).
Second, I used another software (oTree instead of zTree) which also
affected the graphical user interface participants were exposed to.
Third, GMTV gave participants the opportunity to donate to \emph{Doctors
without Borders} whereas I offered carbon dioxide offsets.

The experiment lasted around 25 minutes on average. The earnings
averaged 11.23 Euros (sd = 4.85).\footnote{This value include earnings
  from the incentivized risk elicitation task that is not part of the
  analysis.}

@@

In particular, do the two samples' contributions follow the same path
over the 10 periods they played? The answer is \emph{yes and no}.
Figure~\ref{fig-share-of-contributions} and
Table~\ref{tbl-contribution-periods} illustrate that the samples make
similar contributions at the beginning and the end of the game but
behave differently in between. More precisely, the left panel--depicting
the average contributions in absolute terms--shows that the original
sample contributed more than the reproduction sample \emph{in all but
the first and last period}.\footnote{In period five, this difference is
  significant: a two-sided rank sum test yields p=0.0486.} For this
reason, the original sample's behavior differs from the reproduction
sample's behavior in two aspects: it contributes more and exhibits a
considerable drop in the last period (whereas the reproduction sample's
contributions flatten).

Note that increasing contributions over time imply increasing endowments
over time. Hence, absolute contributions do not tell much about the
willingness to cooperate. For this reason, the right panel in
Figure~\ref{fig-share-of-contributions} shows the average \emph{share of
endowments contributed} over time. Both samples exhibit a similar
pattern: their share of endowments contributed declined and did not
stabilize. However, both samples also differ with respect to one aspect:
the reproduction sample's share of contributions declines faster. This
is mirrored by a two-sided rank sum test which is only significant at a
five percent level in periods three and four.

@@

This is remarkable given the different sample and language, the
different software and user interface as well as the online setting
during the COVID-19 pandemic. The result suggests that by and large, the
sum of these factors did not affect people's preferences towards
cooperation.

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal of Behavioral and Experimental Economics}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation},
  pdfauthor={Hauke Roggenkamp},
  pdfkeywords={Public goods, Dynamic
games, Reproducibility, Generalizability, Online experiment, Climate
change mitigation},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    Public goods \sep Dynamic
games \sep Reproducibility \sep Generalizability \sep Online
experiment \sep 
    Climate change mitigation
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, sharp corners, frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. For example, opting for environmentally friendly policies today
not only reduces carbon dioxide emissions immediately, but also helps us
reach the Paris climate targets tomorrow. Deferring these policies to a
later state, may not necessarily prevent us from reaching these targets,
but it will require more effort in the future compared to a path which
includes immediate action \citep{HaenselEtAl2022}. Aiming at certain
goals, today's actions (or the omission thereof) not only affect
intermediate outcomes but also the number of viable paths one can choose
from that lead to that specific goal.

Public good (or public bad) games---although often intended to inform
climate policies
\citep[e.g.][]{MilinskiEtAl2006, TavoniEtAl2011, Hauser2014, BrickEtAl2015, GomezEtAl2018, CalzolariEtAl2018, CookEtAl2019}---fail
to include these temporal interdependencies simply because participants
have the same set of actions in each period. Accordingly, participants'
actions in a given period do not affect their action space in subsequent
periods. To better capture the lack of realism, consider carbon dioxide
emissions, where the current stock will last for well over a millennium
\citep{Inman2008, CalzolariEtAl2018}. Playing with fresh endowments in
each period is as if one could just undo carbon dioxide emissions at no
cost.

A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
hereafter, GMTV]{GMTV2017} as well as Stefan Große (unpublished), shows
that it is relatively simple to include this element of realism. They
incorporate interdependencies into a \emph{dynamic} public goods game
(dPGG) by defining endowments as the income of previous periods.
Consequently, participants' actions in a given period affect their
number of actions in subsequent periods: the more (less) they earn now,
the more (less) they can contribute in the next period. Importantly,
this modification qualitatively yields the same rational predictions as
the static game (i.e.~free-riding and the under-provision of the public
good). It is thus, equally well suited to study dilemma situations.

As there is surprisingly little experimental research on
interdependencies\footnote{See e.g. \citet{BattagliniEtAl2016},
  \citet{Rockenbach2017} or \citet{Moser2019}.}, I reproduced one of
GMTVs' treatments to compare dynamics across (in)experienced samples to
investigate its generalizability. \citet{GKLS2020} find that static
public goods games do not generalize well to real-world climate action.
They also find that generalizability is dependent on the structural
resemblance of the public goods game with the context of climate change
mitigation: Greater resemblance improves generalizability. Because
GMTVs' dynamic setting has a more realistic property---namely,
interdependencies---one would expect it to be better suited to inform
public policy. As means to test this intuition, I not only ran the
experiment with different samples but also observed the participants'
behavior in voluntary climate actions (VCA).\footnote{The VCA is a
  (charitable) dictator game where each participant is a dictator
  dividing her budget between herself and some organization linked to
  the reduction of CO2 emissions. \citet{EckelGrossman1996} were the
  first to implement a charitable dictator game observing contributions
  of 30\% of the endowments. Like \citet{GKLS2020},
  \citet{CarpenterEtAl2008} report that students make lower
  contributions to charity than community members.} This yielded a
setting similar to the one of \citet{GKLS2020}, which allows me to
analyze how behavior in the abstract game translates into real-world
action across samples. This research shows that the dynamic setting
\emph{does not} add any advances to the generalizability of results.

\citet{AGM2018} conducted static public goods games in the lab and on
MTurk to draw (and report) lessons from online experimentation. This
study extends this literature \citetext{\citealp[see,
e.g.,][\citet{AmirEtAl2012}]{KrantzEtAl1997}; \citealp{KleinEtAl2014}; \citealp{PaolacciChandler2014}; \citealp{GoodmanPaolacci2017}; \citealp{SnowbergYariv_2021}; \citealp{GuptaRigottiWilson_2021}; \citealp{BusoEtAl2021}}
by focusing on an \emph{inconvenient} sample (i.e.~one that is a
completely inexperienced sample \citep[see also][]{BenndorfEtAl2017}
that has not been exposed to interactive experiments before) playing a
computationally more complex game during a time that was characterized
by more inattentiveness in online samples
\citep{ArecharRand2021, PeytonEtAl2022}. With this background in mind,
it required me to design robust (and thus, more complex) software to
minimize attrition. I collected para data \citep[
p.~12]{Parsons2022}---which capture screen time and survey navigation,
for instance---to assess the desired fluency and feasibility of the
experiment. Like \citet{AGM2018}, this research is of practical
relevance as it reports on the robust design that made the dynamic game
feasible.

@@

Today, 20 years later, we have accustomed ourselves to mechanisms
designed to unravel the fuzzy back-and-forth between exploratory and
confirmatory research. Prominently, pre-registrations and pre-analysis
plans (PAP) \citep[see, e.g.,][]{BrodeurEtAl2022} were established as a
means to tie the researchers' hands with respect to p-hacking and
ex-post theorizing when doing confirmatory research---reducing
observable discrepancies between Daryl Bem's above-mentioned (a) and
(b).

While pre-registrations and PAPs could help to make empirical sciences
more credible, they come at costs that are discussed by
\citet{Olken2015}, \citet{PageEtAl2021}, as well as \citet{Krishna2021},
\citet{SimmonsEtAl2021}, and \citet{PhamEtAl2021}. One important concern
is that strict pre-registrations may severely discount any additional
analysis of the data inspired by surprise results. In practice, there
are at least two ways to approach that problem: First, one could (and
should) add unforeseen analyses to the article but be sure to label them
as exploratory. Second, one could write a minimal pre-registration
leaving enough degrees of freedom for the researcher to incorporate such
surprises without further notice. The key difference between the two
approaches is the deliberate omission of transparency.

For the field of neuropsychopharmacology \citet{WaldronAllen2022}
document that the depth of pre-registrations differs indeed: it is
spanning from notes on hypotheses only to fully specified, detailed
experimental protocols with accompanying power analyses and sampling
plans. Treating all pre-registrations equally may thus lead to an
adverse effect: If one can acquire the \emph{`pre-registered'} label
with minimal effort and maximum flexibility, the label itself may run
into danger by becomming worthless and to missing the target of making
science more credible.

This erosion of credibility can be avoided by the means of
transparency---not because transparency can tighten the ties but because
it facilitates scrutiny, policing
\citep[see][]{AnkelPetersFialaNeubauer2023} and forensics \citep[see,
e.g.,][]{SimonsohnEtAl2023}: transparent research practices make it
easier for others to track and understand a researcher's reaction to
surprises within the data, which, in turn, gives the researcher more
flexibility to react to said surprises. As additional transparency is
associated with additional effort, I propose version control as a
natural and easy-to-implement solution augmenting pre-registrations.

Contemporary experimental research is, to a certain degree, a
computational science: experiments often require complex software and
the analysis thereof can result in complicated scripts. In addition,
much research is carried out in collaborative efforts. For these reasons
alone, it makes sense to implement version control systems such as
GitHub and GitLab as well as OSF (albeit less powerful) that ensure that
files are stored consistently and that changes are tracked. When these
systems are implemented throughout the entire research process, one can
archive different states of the software and visualize differences
between different states. For instance, one can archive the analysis
before and after the data was collected or the experimental software
used in a pilot and the eventual experiment. Importantly, one can keep
projects private and change their visibility to public only after the
corresponding article is accepted for publication. Taken together, these
features \emph{automatically} enhance transparency and facilitate
scrutiny, policing, and forensics whilst making software development and
collaboration more efficient. As a consequence, the implementation and
eventual disclosure of version control come not only with
meta-scientific but also with organizational benefits.

The experiment reported in this article qualifies for the
\emph{`pre-registered'} label at first glance: The analysis was
pre-registered in the American Economic Association's RCT Registry
\citep{preregistration}. Furthermore, I pre-registered the exact
analyses I planned to run (PAP) when I designed the experiment on
\href{https://github.com/Howquez/GMTV/tree/July21Replication/analysis/R}{GitHub}.\footnote{bit.ly/3Pnak5H.
  To run the code, you need to execute the .Rmd files in this repository
  in the order that is indicated by file names. Detailed instructions
  can be found in the README file accompanying the analysis scripts.}

At second glance, the analysis that made the most sense after having
collected the data and that is reported here is a little different
though: Because the more representative subject pool was exhausted
earlier than anticipated, I recruited students which opened up a new
research direction: assessing generalizability. Hence, this article
combines both confirmatory as well as exploratory research.

Accordingly, I edited many of the analysis scripts.\footnote{The source
  code of this document contains the analysis and can be found
  \href{https://github.com/Howquez/GMTV/blob/main/analysis/article/paper.qmd}{here}:
  https://bit.ly/43LCyLw} However, because the originally planned
analysis code is archived and reproducieable, these changes are
transparent. Importantly, I followed a literate programming approach
\citep{Knuth_1984, AkhtarYe_2023}. Hence, all documents needed to
analyze the data and to write the report stem from the same source. This
establishes consistence between the commands one tells the statistical
software to do and the explanation one tells human beings one told the
statistical software to do. As such, (a), (b), and the transition from
(a) to (b) are not only transparent but also comprehensible.

@@

In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
well as a \emph{scientific} reproduction\footnote{In fact,
  \citet{Hamermesh2007} uses the term \emph{replication} instead of
  \emph{reproduction}. The reason I deviate is that I do not compare
  different treatments with each other to \emph{replicate} a treatment
  effect. Instead, I \emph{reproduce} the results of one specific
  treatment arm.} of one treatment of GMTVs' dynamic public goods game.
The pure reproduction re-analyzes the original data.
\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
\href{}{the errors I identified} within the original paper. The
scientific reproduction, where I utilize a different sample drawn from a
different population in a different situation, is described in the
following sections.

@@

In the same stroke as GMTV I employ a real giving task after the
abstract game. Specifically, I employed a (charitable) dictator game
where each participant is a dictator dividing her budget between herself
and some organization. Whereas GMTV chose \emph{Doctors without Borders}
as a receiver, I chose another organization in another context: like
\citet{GKLS2020}, I employed a VCA, where participants could donate any
amount of their earnings to offset carbon dioxide (that is, retire
emission permits from the EU ETS).\footnote{Importantly,
  \citet{GKLS2020} made the VCA decision with a fresh endowment
  \emph{before} they played the abstract game. I deviate from their
  procedure to match GMTVs' procedure.} To ensure that each participant
had the same basic level of information about the impact of their
decision, I provided some basic information about the mechanism. The
information also highlighted that the mitigation came into operation on
a European level. Finally, I informed the participants that the
documentation of individual and aggregate contributions was to be posted
immediately after the conclusion of the sessions online. To avoid
privacy or social image concerns, participants learned their unique and
random IDs, which they needed to identify their individual
contributions. The document certified that their contributions have been
used to offset
\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
tons} of carbon dioxide emissions.

@@

Throughout this paper, I will compare the results of my experiment with
the results of GMTVs' NOPUNISH 10 Period treatments. I am thus,
referring to three different samples utilized at two different points in
time: the University of Nottingham's students (in late 2012), Hamburg's
citizens, and the University of Hamburg's students (both in July 2021).
Table~\ref{tbl-sample-properties} gives an overview.

@@

I chose oTree \citep{oTree} to implement the experiment because it is
open-source, well-documented, and very flexible. Its
\href{https://getbootstrap.com/}{Bootstrap} (a powerful frontend
toolkit) integration allowed me to make the graphical user interface
interactive, appealing, and easy to navigate. The
\href{https://www.highcharts.com/}{Highcharts library} additionally made
it easy to visualize results and communicate dynamics. Insofar, oTree
served as a good tool to enhance the participants' user experience and
thus, to make dropouts less likely.

Which features were required to handle dropouts? First, participants had
to be matched to form a group \emph{after} comprehension questions were
answered successfully. Importantly, participants were grouped according
to the order they answered these questions to reduce waiting times.
While waiting for other players to form the group, the participants saw
a wait-page informing them that they are waiting for other participants
to arrive and that they do not have to wait for longer than 10 minutes.
The screen also informed them that they would receive a \emph{patience
bonus} of one Euro after the expiration of that time (or what was left
of it). Second, participants only had 10 minutes to make the first
contribution and 4 minutes for the remaining contributions. After this
time expired, participants were replaced by bots that made random
contributions. In this case, the remaining group members were informed
about the replacement. Both features were implemented to limit wait
times and boredom for other participants. Section~\ref{sec-feasibility}
shows that the first feature became effective in some cases, whereas the
second feature did not.

@@

Overall, I stuck to GMTVs' protocol as close as possible, however, I
deviated in a few aspects. First, the instructions were German and also
covered topics inherent to the online setting (dropouts and bots, for
instance). Second, I used another software (oTree instead of zTree)
which also affected the graphical user interface participants were
exposed to. Third, GMTV gave participants the opportunity to donate to
\emph{Doctors without Borders} whereas I offered carbon dioxide offsets.

The experiment lasted on average for around 25 minutes. The earnings
averaged 11.23 Euros (sd = 4.85).\footnote{This value include earnings
  from the incentivized risk elicitation task that is not part of the
  analysis.}

@@

In particular, do the two samples' contributions follow the same path
over the 10 periods they played? The answer is both \emph{yes and no}.
Figure~\ref{fig-share-of-contributions} and
Table~\ref{tbl-contribution-periods} illustrate that the samples make
similar contributions at the beginning and the end of the game but
behave differently in between. More precisely, the left panel--depicting
the average contributions in absolute terms--shows that the original
sample contributed more than the reproduction sample \emph{in all but
the first and last period}.\footnote{In period five, this difference is
  significant: a two-sided rank sum test yields p=0.0486.} For this
reason, the original sample's behavior differs from the reproduction
sample's behavior in two aspects: it contributes more and exhibits a
considerable drop in the last period (whereas the reproduction sample's
contributions flatten).

Note that increasing contributions over time imply increasing endowments
over time. Hence, absolute contributions do not say much about the
willingness to cooperate. For this reason, the right panel in
Figure~\ref{fig-share-of-contributions} shows the average \emph{share of
endowments contributed} over time. Both samples exhibit a similar
pattern: Their share of endowments contributed declined and did not
stabilize. However, both samples also differ with respect to one aspect:
the reproduction sample's share of contributions declines faster. This
is mirrored by a two-sided rank sum test which is only significant at a
five percent level in periods three and four.

@@

This finding is remarkable given the different sample and language, the
different software and user interface as well as the online setting
during the COVID-19 pandemic. The result suggests that by and large, the
sum of these factors did not affect people's preferences towards
cooperation.
